Identifying Inter-Genomic Repeats Using Fast, Approximate Methods for Betweenness Centrality

### 2015-05-18 manuscript/manuscript.tex
removed benchmark

@@

>>>>

Apart from simulated metagenomic graphs, we study how approximation algorithms for betweenness centrality work on real datasets. We evaluated the runtime  of these algorithms on metagenomic stool sample of a premature infant. This graph has 3797425 nodes and 2970379 edges. We compared the performance of Bambus2's repeat detection module on this data with the performance of approximate betweenness centrality algorithms.

@@

\subsection*{Results On Real Metagenomic Datasets}
We evaluated the runtime of Bambus2's repeat detection module on metagonic stool sample. It
